---
title: "TS | HW1"
author: "Краснов Иван, Тарасова София"
output:
  html_document:
    df_print: paged
---
```{r}
library(readr)
library(dplyr)
library(ggplot2)
library(tibble)

library(forecast)
library(zoo)
library(xts)
library(tseries)
library(pander)
library(Quandl) 
library(stargazer)
library(stats)
library(foreach)
library(fpp2)
library(stringr)
library(knitr)
library(haven)
library(lmtest)
library(foreign)
library(grid)
library(vcd)
library(kableExtra) 
```
```{r}
options(scipen = 999)
```

```{r}
full_data = read_csv("LBMA-SILVER.csv")
```

```{r}
work_data = full_data %>% select("Date","USD") %>% filter(Date > "2020-10-06")
summary(work_data)
```

```{r}
work_data %>% 
  ggplot(aes(USD, fill = "e03450")) + 
  scale_y_continuous(name = "Density") +
   scale_x_continuous(name = "Fixed prices of silver, US dollars") +
  geom_density(alpha = 0.5)
```

```{r}
plot(work_data, ylab = "USD", xlab = "Date", type="o")
```
```{r}
data = work_data
raw = full_data  %>% select("Date","USD")
```


# Descriptive analisys

### Descriptive statistics


```{r}
nam = 'Estimates and Statistics'
n = nrow(data)
mean = round(mean(data$USD),2)
variance = round(var(data$USD),2)
sd = round(sd(data$USD),2)
median = round(median(data$USD),2)
min = round(min(data$USD),2)
max = round(max(data$USD),2)
range = round((max-min),2)

metrics = data.frame(n,mean,median,variance,sd,min,max,range)
metrics %>% kable(format = "html",caption = " Estimates and Statistics ") %>% kable_styling(bootstrap_options = c("striped"))
```

### Base graph


```{r}
data %>%  ggplot(aes(x = as.Date(Date), y = USD)) + 
  geom_line(color = "#69b3a2")  + 
  labs(title = "Fixed prices of silver by LBMA, total",
       x = "", 
       y = "Prices, US dollars",
       caption = 'Source: NASDAQ') + 
  scale_x_continuous(breaks = c(as.Date("2020-10-06"),  as.Date("2021-01-31"),  as.Date("2021-07-31"), as.Date("2022-01-31"))) + 
  scale_y_continuous() + 
  annotate("text", label = "Mean", x = as.Date("2021-05-31"), y = 24.83, size = 3, colour = "black") + 
  geom_line(aes(y = mean, color = 'coral2'), linetype = "dashed") + 
  theme(legend.position ="none")
```

# Testing for stationarity

первый способ сделать тс 

```{r}
ts <- ts(data, frequency = 1, start = c(as.Date(2020-10-06)))
```

второй 

```{r}
series <- xts(data$USD, data$Date)
```

второй смог лучше

###Тестируем нашу выборку без преобразований

```{r}
adf.test(series)
kpss.test(series)
```

###Первая разность 

```{r}
value_old <- as.vector(data$USD)
value_old_changed<-diff(value_old)
value_old_changed<- c(NA,value_old_changed)
data$value_changed <- value_old_changed
```

###Вторая разность:

```{r}
value_2dif <- as.vector(data$value_changed)
value_2dif<-diff(value_2dif)
value_2dif<- c(NA,value_2dif)
data$value_changed_2 <- value_2dif
```

###График первой разности:

```{r}
g4 = data %>% ggplot(aes(x = as.Date(Date), y = value_old_changed)) + 
  geom_line(color = "#69b3a2")  + 
  labs(title = "1 diff of prices, US dollars",
       x = "", 
       y = "") + 
  scale_x_continuous(breaks = c(as.Date("2020-10-06"),  as.Date("2021-01-31"),  as.Date("2021-07-31"), as.Date("2022-01-31"))) + 
  scale_y_continuous() + 
  theme(legend.position = "none")
g4
```

###График второй разности:

```{r}
g4_2 = data %>% ggplot(aes(x = as.Date(Date), y = value_changed_2)) + 
  geom_line(color = "#69b3a2")  + 
  labs(title = "2 diff of prices of silver",
       x = "", 
       y = "2 diff of prices, US dollars") + 
  scale_x_continuous(breaks = c(as.Date("2020-10-06"),  as.Date("2021-01-31"),  as.Date("2021-07-31"), as.Date("2022-01-31"))) + 
  scale_y_continuous() + 
  theme(legend.position = "none")
g4_2
```
#Testing of 1 diff

```{r}
dif1 <- data %>% dplyr::select(Date, value_changed)

library(zoo)
dif1$Date <- as.Date(dif1$Date)

series_dif1 <- xts(dif1$value_changed, dif1$Date)

series_dif1 <- na.omit(series_dif1)

dif1 <- na.omit(dif1)
```

```{r}
adf.test(series_dif1)
kpss.test(series_dif1)
```
## Вторая разность:

```{r}
dif2 <- data %>% dplyr::select(Date, value_changed_2)

series_dif2 <- xts(dif2$value_changed_2, dif2$Date)

series_dif2 <- na.omit(series_dif2)
```

```{r}
adf.test(series_dif2)
kpss.test(series_dif2)
```

## Лог диффы:

```{r}
log_dif_old <- diff(log(value_old), lag = 1)
log_dif_old<- c(NA,log_dif_old)
data$log_dif_old <- log_dif_old
```

```{r}
logdif <- data %>% dplyr::select(Date, log_dif_old)

series_logdif <- xts(logdif$log_dif_old, logdif$Date)

series_logdif <- na.omit(series_logdif)

adf.test(series_logdif)
kpss.test(series_logdif)
```
```{r}
ts_final = series_dif1



```

# Modelling

### Fitiing and examing results

## PACF

```{r}
pacf1 <- pacf(dif1$value_changed, plot = FALSE)
plot(pacf1, main = "PACF")
```

## ACF

```{r}
acf1 <- acf(dif1$value_changed, plot = FALSE)
plot(acf1, main = "ACF")
```


Следовательно, 


### Data partition

```{r}
fitting1 <- ts_final["2020-10-06/2021-08-06"]
validation1 <- ts_final["2021-08-09/2021-11-08"]
testing1 <- ts_final["2021-11-09/2022-02-10"]
```


```{r}
phat <- 3
qhat <- 3

# setting critical level(s)
alpha <- 0.05

# other shortcuts
N    <- length(fitting1) # number of obs in the transformed series
pq   <- expand.grid(0:phat,0:qhat) # all combinations of (p,q)
M    <- nrow(pq) # number of specifications
Lhat <- 5 # max lags to use in residual ACF analysis


 ## Estiamte all the ARMA and collect the results

SKIPm <- c(0) # the specs to skip (if there are errors or something)

#loop over all the combinations of (p,q) and estimate the ARMAs
ARMAs1 <- foreach(m=seq(1:M)[!(1:M %in% SKIPm)], .combine=rbind) %do% {
  
  # the orders
  p_ <- pq[m,1]
  q_ <- pq[m,2]
  
  # the estimates
  armapq <- arima(fitting1, c(p_,0,q_), method="ML")
  
  # the AR part coefficients (only valid for p>0)
  if(p_>0) {arcoefpq <- armapq$coef[1:p_]}
  
  # stationarity of AR part (only valid for p>0, TRUE for p=0)
  if(p_>0) {
    statAR <- sum(abs(polyroot(c(1,-arcoefpq)))>1)==p_
  } else {
    statAR <- TRUE
  }
  
  # the residuals
  respq <- armapq$residuals
  
  # the LB test results
  LBpvalpq <- Box.test(respq[-1], lag = Lhat, type = c("Ljung-Box"), fitdf=p_+q_)$p.value

  # info criteria
  aicpq <- AIC(armapq)
  bicpq <- AIC(armapq, k=log(N))
  
  # combine the results together
  data.frame(m    = m,         # spec number
    p    = p_,        # AR order
    q    = q_,        # MA order
    stat = statAR,    # AR part stationarity check
    LB   = LBpvalpq,  # LB test p-value
    AIC  = aicpq,     # AIC
    SBIC = bicpq)     # SBIC
}

# all the results
# print(ARMAs)

# remove invalid LB test results
ARMAs1 <- ARMAs1[!is.nan(ARMAs1$LB),]

# keep only stationary & without residual correlation 
ARMAs1 <- ARMAs1[ARMAs1$stat == 1 & ARMAs1$LB >= alpha,] 

# sort by SBIC (keep top-5)
ARMAs1[order(ARMAs1$SBIC)[1:5],]

ARMAs3_3 <- foreach(m = ARMAs1[order(ARMAs1$SBIC)[1:5],1]) %do% {
  arima(fitting1, c(pq[m,1],0,pq[m,2]))
}

```

### Validation

```{r, warning=FALSE, message=FALSE, results='asis'}
forecasts1 <- foreach(m = ARMAs3_3[1:5], .combine = cbind) %dopar% {
  forecast(m, h = length(validation1))$mean
}
```

# Asymmetric loss function

```{r}
ALF <- function (x) {
  ifelse (x < 0, return(abs(x)), return(1.5 * x))
}
```

We consider symmetric and asymmetric loss functions
```{r, warning=FALSE, message=FALSE, results='asis'}
#symmetric
MAPE1 <- foreach(m = forecasts1[,1:5], .combine = cbind) %dopar% {
  sum(abs((validation1 - m)/validation1))/length(validation1)
}

#asymmetric loss function
ALF1 = list()
ALF11 = 0
j = 1
while (j <= 5){
  for (i in (1:3)){
    ALF11 = ALF11 + ALF(as.data.frame(validation1)$V1[i] - as.data.frame(forecasts1)[i,j])/length(as.data.frame(validation1)$V1)
  }
  ALF1 = append(ALF1, ALF11)
  j = j + 1
  ALF11 = 0
}

error1 <- rbind.data.frame('MAPE' = MAPE1, "ALF" = ALF1)
                    
error1
``` 

### Testing


```{r, warning=FALSE, message=FALSE, results='asis'}
model1 = arima(fitting1, c(0,1,0))
forecasts1<- forecast(model1, h = length(testing1))$mean
model2 = arima(fitting1, c(1,0,1))
forecasts2 <- forecast(model2, h = length(testing1))$mean
model3 = arima(fitting1, c(0,5,1))
forecasts3 <- forecast(model3, h = length(testing1))$mean
model4 = arima(fitting1, c(1,2,0))
forecasts4 <- forecast(model4, h = length(testing1))$mean
```


### All forecasts 

```{r}

test_forecasts = data_frame("ARMA(0,0)" = forecasts1,
                            "ARMA(1,1)" = forecasts2,
                            "ARMA(0,1)" = forecasts3,
                            "ARMA(1,0)" = forecasts4)
for (i in c(3:4)){
  test_forecasts[1,i] = test_forecasts[1,i] + dif1$value_changed[341]
}

for (i in c(3:4)){
  test_forecasts[2,i] = test_forecasts[2,i] + test_forecasts[1,i]
}

for (i in c(3:4)){
  test_forecasts[3,i] = test_forecasts[3,i] + test_forecasts[2,i]
}


test_forecasts$value = dif1$value_changed[341]

head(test_forecasts)
```

```{r}
MAPE <- foreach(m = test_forecasts[,1:4], .combine = cbind) %dopar% {
  sum(abs((test_forecasts$value - m)/test_forecasts$value))/length(test_forecasts$value)
}

ALF_test = list()
ALF_test_1 = 0
j = 1
while (j <= 4){
  for (i in (1:4)){
    ALF_test_1 = ALF_test_1 + ALF(test_forecasts$value[i] - test_forecasts[i,j])/length(test_forecasts$value)
  }
  ALF_test = append(ALF_test, ALF_test_1)
  j = j + 1
  ALF_test_1 = 0
}

error <- rbind.data.frame('MAPE' = MAPE, 'ALF' = unname(ALF_test))
                    
error
```

## Выбираем ARMA(1,1) 

# Residuals

```{r}
arma <- Arima(data$USD, order = c(1,0,1))

forec_raw_data = forecast(arma, h = length(data$USD))

resid = as.data.frame(forec_raw_data$residuals)
resid = resid %>% 
  mutate(abs = abs(x)) %>% 
  mutate(squared = x^2)

loss = data.frame(forec = forec_raw_data$mean, resid = forec_raw_data$residuals)
ggplot(loss) +
  geom_point(aes(x = forec, y = resid), col = 'red')

ggplot(resid) +
  geom_point(aes(x = x, y = abs), col = 'red')

ggplot(resid) +
  geom_point(aes(x = x, y = squared), col = 'red')

acf(ts(forec_raw_data$residuals), main ='Residuals MA(1)')

checkresiduals(arma)
box = Box.test(forec_raw_data$residuals, lag = 3.26, type = "Ljung-Box")
```
```{r}
forecast = data.frame("Time" = data$Date,
                      "Value" = data$USD,
                      "Forecast" = forec_raw_data$mean,
                      "Fitted" = fitted(arma),
                      "Lower" = forec_raw_data$lower,
                      "Upper" = forec_raw_data$upper)

ggplot(forecast, aes(x = Time)) +
  geom_line(aes(y = Value), col = 'red')  +
  geom_line(aes(y = Fitted), col = 'green') +
  ggtitle ("ARMA (1,0,1)  fitting") +
  theme_minimal() + 
    labs(x = " ", y = "")
```

```{r}
ggplot(forecast, aes(x = Time)) +
  geom_line(aes(y = Forecast), col = 'blue')  +
  geom_line(aes(y = Upper.95.), col = 'pink') +
  geom_line(aes(y = Lower.95.), col = 'violet') +
  ggtitle ("ARMA (1,0,1)  forecast") +
  theme_minimal() + 
    labs(x = " ", y = "")
```



#Predictions and graphs
```{r}
arma <- arima(series, order = c(1,0,1))
forecast_2022half <- forecast(arma, h = 180)

 past <- ts(series)

autoplot(forecast_2022half) + autolayer(past)

```

```{r}
accuracy(forecast_2022half)
```

